Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-15 paper/main.tex
cleaning before printing

% RSC + LOC
Apart from the PPA, we find significantly increased activity in the dorsal
precuneus and posterior cingulate region (e.g. retrosplenial complex; RSC) and
lateral occipital cortex (LOC; more lateral in the AV stimulus, more medial in
the AD stimulus) across contrasts of both naturalistic stimuli.
% RSC intro
Like the PPA, the RSC and LOC repeatedly showed increased hemodynamic activity
in studies investigating visual spatial perception or navigation (see
\citep{chrastil2018heterogeneity, bettencourt2013role} for reviews).
% not random shit
Thus, our approach to operationalize spatial perception based on stimulus
annotations did not lead to significant clusters scattered across the brain but
restricted to a brain network that is assumed/known to be involved in (visual)
spatial perception and cognition.
%
This suggest that model-driven methods based on stimulus annotations are
suitable to reveal spatially concise functional areas and networks.
%
Nevertheless, ``cleanliness''/``neatness``  of results (i.e. the signal-cluster
to noise-cluster ration)\todo{if you know what I mean} depends on how many
events correlating with an assumed perceptual process the stimulus provides
and to the extent to which a naturalistic stimulus' multi-dimensionality is
annotated and statistically controlled.

@@

% natural stimulation
Natural stimuli like movies \citep{eickhoff2020towards,
hasson2008neurocinematics, sonkusare2019naturalistic} or narratives
\citep{hamilton2018revolution, honey2012not, lerner2011topographic,
silbert2014coupled, wilson2008beyond} offer an easy to implement, (continuous,)
complex, immersive, task-free paradigm that more closely resembles our natural
dynamic environment than traditional experimental designs.

>>>>

% RSC + LOC
Apart from the PPA, results revealed significantly increased activity in the
dorsal precuneus and posterior cingulate region (e.g. retrosplenial complex;
RSC) and lateral occipital cortex (LOC; more lateral in the AV stimulus, more
medial in the AD stimulus) across contrasts of both naturalistic stimuli.
% RSC intro
Like the PPA, the RSC and LOC repeatedly showed increased hemodynamic activity
in studies investigating visual spatial perception or navigation (see
\citep{chrastil2018heterogeneity, bettencourt2013role} for reviews).
% not random shit
Thus, our approach to operationalize spatial perception based on stimulus
annotations did not lead to significant clusters scattered across the brain but
restricted to a brain network that is assumed/known to be involved in (visual)
spatial perception and cognition.
%
This suggest that model-driven methods based on stimulus annotations are
suitable to reveal spatially concise functional areas and networks.
%
Nevertheless, ``cleanliness''/``neatness``  of results (i.e. the signal-cluster
to noise-cluster ration)\todo{if you know what I mean} depends on how many
events correlating with an assumed perceptual process the stimulus provides and
to the extent to which a naturalistic stimulus' multi-dimensionality is
annotated and statistically controlled.

@@

% natural stimulation
Natural stimuli like movies \citep{eickhoff2020towards,
hasson2008neurocinematics, sonkusare2019naturalistic} or narratives
\citep{hamilton2018revolution, honey2012not, lerner2011topographic,
silbert2014coupled, wilson2008beyond} offer an easy to implement, (continuous,)
complex, immersive, task-free paradigm that more closely resembles our natural
dynamic environment than traditional experimental designs.
%
Here, we operationalized the perception of spatial information based on
annotated stimulus features embedded in two naturalistic stimuli and compared
current results to results gained from a traditional visual localizer.
%

Here, we reused three fMRI datasets and two stimulus annotations that are part
of the studyforrest dataset \href{http://www.studyforrest.org}{studyforrest.org}
to operationalize the perception of spatial information embedded in two
naturalistic stimuli and to compare current results to results gained from a
traditional visual localizer paradigm.
